SNP Analysis

### 2018-09-07 snp/SNP_Prediction_Analysis.Rmd
Adding QC to pipeline

pred.qc = pred.qc %>% group_by(Status, Samplename) %>% dplyr::mutate(
  lowsca = ( Status == 'P' & (`mean(SCA.Ratio)` < 0.03 & `mean(Purity)` >= 0.95))
)

# pred.qc = pred.qc %>% group_by(Status, Samplename) %>% dplyr::mutate(
#   lowsca = ( `mean(SCA.Ratio)` < 0.01 & `mean(Purity)` >= 0.95)
# )

#table(subset(pred.qc, !lowsca)$Status)/table(pred.qc$Status)

ggplot(pred.qc, aes(`mean(SCA.Ratio)`, `mean(Purity)`, color=Status)) + geom_point() + facet_grid(~Status) + 
  geom_vline(xintercept=0.01) + geom_hline(yintercept = 0.95)

@@

ggplot(pred.qc, aes(Prob)) + geom_histogram(aes(fill=..x..), breaks=seq(0,1,0.1) , show.legend = F) +
  scale_fill_gradientn(colors = myPal,  name='') + 
  labs(title='Predictions, all samples model', y='n Samples', x='Unadjusted Probability')

@@

ggplot(subset(pred.qc, !exclude & !wgd & !lowsca), aes(`mean(Purity)`,Prob, color=Risk, shape=Status)) + 
  facet_grid(~Status) + geom_point()

@@

# Quick check
# nrow(subset(ex.pred, Prob > 0.5 & Status == 'P'))/table(ex.pred$Status)['P']
# nrow(subset(ex.pred, Prob < 0.5 & Status == 'P'))/table(ex.pred$Status)['P'] #False negatives
# 
# nrow(subset(ex.pred, Prob > 0.5 & Status == 'NP'))/table(ex.pred$Status)['NP'] # False pos
# nrow(subset(ex.pred, Prob < 0.5 & Status == 'NP'))/table(ex.pred$Status)['NP'] #
```

@@

```{r loo, eval=T}

>>>>

# pred.qc = pred.qc %>% group_by(Status, Samplename) %>% dplyr::mutate(
#   lowsca = ( Status == 'P' & (`mean(SCA.Ratio)` < 0.03 & `mean(Purity)` >= 0.95))
# )

pred.qc = pred.qc %>% group_by(Status, Samplename) %>% dplyr::mutate(
  lowsca = ( `mean(SCA.Ratio)` < 0.03 & `mean(Purity)` >= 0.95)
)

ggplot(pred.qc, aes(`mean(SCA.Ratio)`, `mean(Purity)`, color=Status)) + geom_point() + facet_grid(~Status) + 
  geom_vline(xintercept=0.03) + geom_hline(yintercept = 0.95)

table(subset(pred.qc, !lowsca)$Status)
table(subset(pred.qc, !lowsca)$Status)/table(pred.qc$Status)

@@

@@

@@

# Quick check
# nrow(subset(ex.pred, Prob > 0.5 & Status == 'P'))/table(ex.pred$Status)['P']
# nrow(subset(ex.pred, Prob < 0.5 & Status == 'P'))/table(ex.pred$Status)['P'] #False negatives
# 
# nrow(subset(ex.pred, Prob > 0.5 & Status == 'NP'))/table(ex.pred$Status)['NP'] # False pos
# nrow(subset(ex.pred, Prob < 0.5 & Status == 'NP'))/table(ex.pred$Status)['NP'] #

ct = cor.test(pred.qc.ex$Prob, pred.qc.ex$`mean(SCA.Ratio)`)
ct2 = cor.test(pred.qc$Prob, pred.qc$`mean(SCA.Ratio)`)
```

The risk probability is correlated with the % of the genome that's been altered as identified by Xiahong, R=`r ct$estimate` and that's true even when no patients are excluded (R=`r ct2$estimate`).

@@

```{r loo, eval=F}
